Deep Learning

### 2015-03-30 deepreview.tex
a coupe more fixes

The idea that this could be done, and that it worked, was discovered independently by
several different groups in the 1970s and
1980s~\citep{Werbos74,Parker85,LeCun85,RHW}. It spurred a wave of interest for
neural networks, becoming quite popular in the late 1980s, but fell out of favor
between the mid 1990s until its rennaissance in the late 2000s.

@@

Since the early 2000s, ConvNets have been applied with great 
success to the detection, segmentation, and
recognition of objects and regions in images. These were all
tasks in which labeled data was relatively abundant, such as traffic
sign recognition~\cite{sermanet-ijcnn-11,Ciresan-et-al-2012}, the
segmentation of biological images~\cite{ning-05} particularly for
connectomics~\cite{Turaga2010}, and the detection of faces, text,
pedestrians, and human bodies in natural
images~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95,garcia-delakis-04,osadchy-07,
  nasse-09,fan-pami-2010,sermanet-cvpr-13,Tompson-et-al-arxiv2014}.
A major practical success of ConvNets in recent times is face
recognition~\citep{taigman-cvpr-2014}. A recent stunning demonstration
of ConvNets is the generation of image captions, as shown in
Figure~\ref{fig:caption-generation}.

An important application is the labeling of images at the pixel level,
the applications of which include autonomous mobile robots and
self-driving cars~\cite{hadsell-jfr-09,farabet-icml-12}. Companies
such as Mobileye and NVIDIA are using ConvNets in their upcoming
vision systems for cars.  Other applications of ConvNets that are
gaining importance concern natural language
understanding~\citep{collobert:2011b}, and speech
recognition~\cite{Sainath-et-al-ICASSP2013}.

Despite these successes, ConvNets were largely forsaken by the
mainstream computer vision and machine learning communities until the
ImageNet competition in 2012.  When deep convolutional networks were
applied to a dataset of about a million images from the web that
contained a thousand different classes they achieved spectacular
results, almost halving the error rates of the best competing
approaches~\citep{Krizhevsky-2012-small}.  This success came from
efficient use of GPUs, ReLUs, and a new regularization technique
called ``dropout'' ~\citep{Srivastava14} which prevented overfitting
in the fully connected layers.  This success has brought about a
revolution in computer vision, and ConvNets are now the dominant
approach for almost all recognition and detection
tasks~\citep{sermanet-iclr-14,girshick-cvpr-2014,taigman-cvpr-2014,simonyan-arxiv-2014,szegedy-2014,Tompson-et-al-arxiv2014}.

>>>>

The idea that this could be done, and that it worked, was discovered independently by
several different groups in the 1970s and
1980s~\citep{Werbos74,Parker85,LeCun85,RHW}. It spurred a wave of interest for
neural networks, becoming quite popular in the late 1980s, but falling out of favor
between the mid 1990s until their rennaissance in the late 2000s.

@@

Since the early 2000s, ConvNets have been applied with great 
success to the detection, segmentation, and
recognition of objects and regions in images. These were all
tasks in which labeled data was relatively abundant, such as traffic
sign recognition~\cite{sermanet-ijcnn-11,Ciresan-et-al-2012}, the
segmentation of biological images~\cite{ning-05} particularly for
connectomics~\cite{Turaga2010}, and the detection of faces, text,
pedestrians, and human bodies in natural
images~\cite{vaillant-monrocq-lecun-94,nowlan-platt-95,garcia-delakis-04,osadchy-07,
  nasse-09,fan-pami-2010,sermanet-cvpr-13,Tompson-et-al-arxiv2014}.
A major practical success of ConvNets in recent times is face
recognition~\citep{taigman-cvpr-2014}.

An important application is the labeling of images at the pixel level,
the applications of which include autonomous mobile robots and
self-driving cars~\cite{hadsell-jfr-09,farabet-icml-12}. Companies
such as Mobileye and NVIDIA are using such ConvNets-based methods in
their upcoming vision systems for cars.  Other applications of
ConvNets that are gaining importance concern natural language
understanding~\citep{collobert:2011b}, and speech
recognition~\cite{Sainath-et-al-ICASSP2013}.

Despite these successes, ConvNets were largely forsaken by the
mainstream computer vision and machine learning communities until the
ImageNet competition in 2012.  When deep convolutional networks were
applied to a dataset of about a million images from the web that
contained a thousand different classes they achieved spectacular
results, almost halving the error rates of the best competing
approaches~\citep{Krizhevsky-2012-small}.  This success came from
efficient use of GPUs, ReLUs, and a new regularization technique
called ``dropout'' ~\citep{Srivastava14} which prevented overfitting
in the fully connected layers.  This success has brought about a
revolution in computer vision, and ConvNets are now the dominant
approach for almost all recognition and detection
tasks~\citep{sermanet-iclr-14,girshick-cvpr-2014,taigman-cvpr-2014,simonyan-arxiv-2014,szegedy-2014,Tompson-et-al-arxiv2014}
and approach human performance on some tasks. A recent stunning
demonstration combines ConvNets and neural net modules for the
generation of image captions, as shown in
Figure~\ref{fig:caption-generation}.
